---
title: "Add a Theme"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Rmarkdown includes a number of themes as described on the [rmarkdown site](http://rmarkdown.rstudio.com/html_document_format.html#appearance_and_style). 

To add a theme specify the following at the beginning or towards the end of the `_site.yml`. It makes sense to include it near the top as it saves on scrolling when you want to change it (and you will). 

```{r eval=FALSE}
output:
  html_document:
    theme: flatly
    highlight: textmate
```

At the time of writing the available themes that you might want to try are `cerulean`, `cosmo`, `flatly`, `journal`, `lumen`, `paper`, `readable`, `sandstone`, `simplex`, , `spacelab`, `united`, `yeti` (the following were not available `cyborg`, `darkly`, `slate`, `superhero`). See the [rmarkdown site](http://rmarkdown.rstudio.com/html_document_format.html#appearance_and_style) and the [Bootswatch site](http://bootswatch.com) for the theme origins with the wildly popular [bootstrap](http://getbootstrap.com). If none of that makes much sense, it will do when you read up on the links. 



